Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-18 paper-webserver.tex
ADD: main points for the web design para, need to rewrite though

We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google.
The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, by Facebook, as a single-page application to allow efficient data-flow without reloading the website.

>>>>

The front-end website displayed to users is written using the React JavaScript library \url{https://facebook.github.io/react/} as a single-page application to allow efficient data-flow without reloading the website.
To ensure a familiar user interface, we followed the Material Design specification \url{https://material.io/}, published by Google, and follow a card-based design.
(see Figure \ref{fig-results})
While data storage is graph-based, the results of various analysis modules are presented to users in a familiar tabular structure and available for download.
(see Figure \ref{fig-tables})

\begin{figure}[t]
\begin{center}
\includegraphics{images/results.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-results}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics{images/tables.png}
\end{center}
\caption{Caption for figure within column.}
\label{fig-tables}
\end{figure}
